### 2021-07-08 newvariant.tex
one more para

Finally, we synthesize our findings and illustrate the differences between constant-strength and constant-speed interventions using epidemic simulations using the renewal equation (\fref{control_sim}).

>>>>

Finally, we synthesize our findings and illustrate the differences between constant-strength and constant-speed interventions using epidemic simulations using the renewal equation (\fref{control_sim}).
In particular, we consider a scenario in which a new variant is emerging ($\rv > 0\pday$ and $\Rw > 1$) while the incidence of infections caused by the wild type is constant ($\rw = 0\pday$ and $\Rw =1$) before interventions are reduced.
The constant-strength intervention then reduces both $\Rw$ and $\Rv$ by a constant factor $\theta$ beginning day 30, 
whereas the constnat-speed intervention isolates individuals infected with both the wild type and the variant at a constant hazard $\phi$ after day 30.
If the variant has a longer mean generation interval, the consant-strength intervention fails to suppress the spread of the variant (\fref{control_sim}A) because a stronger intervention ($>\phi$) to reduce a higher pre-intervention reproduction number below 1 (\fref{control_sim}B).
